intro

### 2022-02-09 06_Paper/ER-ED/Manuscript_ERED_Stage1.Rmd
added supplement

>>>>

\includepdf[pages={-}, landscape=true]{Supplement/StimList_Suppl.pdf}

## Pilot study: Subjective arousal in the conditions "active viewing - neutral" and "active viewing - negative"

ANOVA:
<br>
`r afex::nice(SubjArousalView_aov)%>% knitr::kable(x = .)`, $BF10=$ `r round(extractBF(SubjArousalView_BF)$bf, digits = 2)`

Paired contrasts:
```{r, echo=FALSE, message=FALSE, warning=FALSE}
apa_table(
  SubjArousalView_con,
  caption = "Paired contrasts for the rmANOVA comparing subjective arousal of negative and neutral pictures in the condition active viewing.",
  note = , 
  escape = FALSE,
  placement = "H"
)
```
Figure:
